Exploring the Shadows of Terror: The Influence of Terrorism on Public Opinion and Democratic Values

### 2024-02-14 outputs/paper/paper.qmd
added scripts

```{r fig.width=15, fig.height=16}
#| label: fig-terrorism-trend
#| fig-cap: Summary of Data Included in theMeta-Analysis
#| echo: false
#| warning: false
#| message: false

# make sure the PATH is right in your setup
# since paper.qmd is under outputs/paper/ folder, we have to jump to parent dir twice
PATH = "../../inputs/data/02-metaanalysis-data.xlsx"

dat <- read_excel(PATH, sheet = "Data",  col_names = TRUE, skip = 3)
dat_studies <- dat[c(1:87)] #studies.
dat_studies <- group_by(dat_studies, ID_RS) %>% slice(1)

### dataframe of reports
dat_reports <- dat[c(1:87)] #reports/publications.
dat_reports <- group_by(dat_reports, ID_R) %>% slice(1)

### set wished layout settings
mytheme <- theme(plot.title = element_text(face = "bold", size = (22), colour = "black"), 
                 axis.text = element_text(size = (18), colour = "black"),
                 axis.ticks.length = unit(0.5, "cm"),
                 axis.title.y = element_text(size = (22), colour = "black"),
                 axis.title.x = element_text(size = (22), colour = "white"))

# Figure 2A
StudyYear <- ggplot(dat_studies, aes(x=StudyYear)) + 
  geom_histogram(binwidth=1,
                 color="#000000", fill="#939598") +
  labs(x="to fill some space", y = "", title = "Year of Data Collection") +
  scale_y_continuous(breaks = c(0, 5, 10, 15, 20, 25, 30, 35, 40, 45)) +
  scale_x_continuous(breaks = c(1985,1990,1995,2000,2005,2010, 2015,2020)) +
  theme_classic() #histogram year of study 
StudyYear <- StudyYear + geom_vline(xintercept=2001, linetype="dashed", size = 1) #add 9/11 line
StudyYear <- StudyYear + geom_vline(xintercept=2004, linetype="dashed", size = 1) #add line
StudyYear <- StudyYear + geom_vline(xintercept=2015, linetype="dashed", size = 1) #add ISIS line
StudyYear <- StudyYear + geom_label(data = dat_studies, 
                                    aes(x=2001, y=27, label = "9/11"),
                                    size=8) #add 9/11 label
StudyYear <- StudyYear + geom_label(data = dat_studies, 
                                    aes(x=2007, y=35, label = "Madrid & \n Israel-Palestine"),
                                    size=6) #add label
StudyYear <- StudyYear + geom_label(data = dat_studies, 
                                    aes(x=2014, y=44, label = "IS Attacks"),
                                    size=8) #add ISIS label
StudyYear <- StudyYear + mytheme

## Figure 2B
PubYear <- ggplot(dat_reports, aes(x=Year)) + 
  geom_histogram(binwidth=1, 
                 color="#000000", fill="#939598") +
  labs(title ="Year of Publication", x = "to fill some space", y = "") +
  scale_y_continuous(breaks = c(0, 5, 10, 15, 20, 25, 30, 35, 40, 45)) +
  scale_x_continuous(breaks = c(1985,1990,1995,2000,2005,2010, 2015,2020)) +
  theme_classic() #histogram year of study 
PubYear <- PubYear + geom_vline(xintercept=2001, linetype="dashed", size = 1) #add 9/11 line
PubYear <- PubYear + geom_vline(xintercept=2015, linetype="dashed", size = 1) #add ISIS France line
PubYear <- PubYear + geom_label(data = dat_reports,
                                aes(x=2001, y=27, label = "9/11"),
                                size=8) #add 9/11 label
PubYear <- PubYear + geom_label(data = dat_reports, 
                                aes(x=2014, y=44, label = "IS Attacks"),
                                size=8) #add ISIS label
PubYear <- PubYear + mytheme

# wrangling
dat$TerrorMeasure[dat$IV_Code==1] <- "Acts of violence"
dat$TerrorMeasure[dat$IV_Code==2] <- "Acts of violence"
dat$TerrorMeasure[dat$IV_Code==3] <- "Threat"
dat$TerrorMeasure[dat$IV_Code==4] <- "Threat"
dat$TerrorMeasure[dat$IV_Code==5] <- "Other"
dat$TerrorMeasure[dat$IV_Code==6] <- "Reported exposure"
dat$TerrorMeasure[dat$IV_Code==7] <- "Reported exposure"
dat$TerrorMeasure[dat$IV_Code==8] <- "Reported exposure"
dat$TerrorMeasure[dat$IV_Code==9] <- "Threat"
dat$TerrorMeasure[dat$IV_Code==10] <- "Threat"
dat$TerrorMeasure[dat$IV_Code==11] <- "Fear"
dat$TerrorMeasure[dat$IV_Code==12] <- "Anger"
dat$TerrorMeasure[dat$IV_Code==13] <- "Other"
dat$TerrorMeasure[dat$IV_Code==14] <- "Other"
dat$TerrorMeasure[dat$IV_Code==15] <- "Other"
dat$TerrorMeasure[dat$IV_Code==16] <- "Other"

dat$TerrorMeasure <- as.factor(dat$TerrorMeasure)

#visualization: Figure 2C
tmdat <- data.frame(prop.table(table(dat$TerrorMeasure)))
TerrorMeasures <- ggplot(tmdat, aes(x = reorder(Var1, -Freq), y = Freq)) +
  geom_bar(stat="identity", width=0.7,
           color="#000000", fill="#939598") +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
  scale_y_continuous(labels = scales::percent,
                     limits = c(0,.6),
                     breaks = c(0,.1,.2,.3,.4,.5,.6)) +
  labs(title = "Terrorism Measures", x="", y = "") +
  theme_classic() 
TerrorMeasures <- TerrorMeasures + mytheme

#wrangling
dat$TerrorType[dat$Type==0] <- "No ideology"
dat$TerrorType[dat$Type==1] <- "Islamist"
dat$TerrorType[dat$Type==2] <- "Extreme right"
dat$TerrorType[dat$Type==3] <- "Other"
dat$TerrorType[dat$Type==4] <- "Other"
dat$TerrorType[dat$Type==5] <- "State terror"
dat$TerrorType[dat$Type==6] <- "Other"
dat$TerrorType <- as.factor(dat$TerrorType)

#visualization: Figure 2D
ttdat <- data.frame(prop.table(table(dat$TerrorType)))
TerrorType <- ggplot(ttdat, aes(x = reorder(Var1, -Freq), y = Freq)) +
  geom_bar(stat="identity", width=0.7,
           color="#000000", fill="#939598") +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
  scale_y_continuous(labels = scales::percent,
                     breaks = c(0,.1,.2,.3,.4,.5,.6)) +
  labs(title = "Type of Terrorism", x = "", y = "") +
  theme_classic() 
TerrorType <- TerrorType + mytheme

# jpeg("Fig2.jpeg", width = 15, height = 16, units = 'in', res = 300)
ggarrange(StudyYear, PubYear, 
          TerrorMeasures, TerrorType,
          labels = c("(A)", "(B)", "(C)", "(D)"),
          font.label = list(size = 22, color = "black"),
          ncol = 2, nrow = 2) #arrange all plots
# dev.off() #safe picture in high resolution.

# 
# StudyYear <- StudyYear + theme(aspect.ratio = 1) + theme(axis.text.x = element_text(size = 5))
# PubYear <- PubYear + theme(aspect.ratio = 1) + theme(axis.text.x = element_text(size = 5))
# TerrorMeasures <- TerrorMeasures + theme(aspect.ratio = 1) + theme(axis.text.x = element_text(size = 5))
# TerrorType <- TerrorType + theme(aspect.ratio = 1) + theme(axis.text.x = element_text(size = 5))
# 
# # Combine the plots into a 2x2 grid
# combined_plot <- (StudyYear | PubYear) / 
#                  (TerrorMeasures | TerrorType)
# 
# # Save the combined plot
# # ggsave("combined_plot.png", combined_plot, width = 10, height = 10)
# combined_plot
```

@@

Diverse Reactions to Ideological Terrorism
Outgroup Hostility: Our analysis, represented in @fig-reactions-to-terrorism, underscores that while all forms of ideological terrorism lead to outgroup hostility, the response is strongest in the face of Islamist terrorism. This could reflect media portrayal and public perception biases, where Islamist acts are more closely associated with the concept of terrorism. Interestingly, other ideologies, or the absence of an ideological label, provoke less intense reactions, suggesting a nuanced public sensitivity to the context and framing of terrorist events.

Conservative Shift: A conservative shift in public opinion was noted across all ideological forms of terrorism, but it was less pronounced for 'No ideology' cases. This suggests that the presence of a clear ideological motive in terrorism might be a key driver in swaying public opinion towards conservative policies and viewpoints.

Impact of Research Design on Perceived Threat
Rally Effects: When examining the influence of research design, experimental designs showed a more marked rally effect compared to cross-sectional studies. This difference indicates that the controlled environment of an experiment, often simulating a direct terrorism threat, might amplify the unifying sentiment among the participants.

Influence of Sample and Country Specifics
General Population vs. Targeted Samples: The general population samples showed a more consistent increase in outgroup hostility and conservatism across the board, as opposed to student or convenience samples. This highlights the importance of sample representativeness in gauging the true pulse of public opinion in response to terrorism.

Geographic Variations: The country-specific analysis revealed that the United States and Israel, both countries with prolonged experiences of terrorism, showed stronger correlations across all three measures compared to other countries. This may be attributed to the higher frequency of terrorist incidents and the consequent heightened public awareness and reaction in these nations.

Guilt-by-Association Effects
Lastly, the 'Guilt-by-Association' section of @fig-reactions-to-terrorism provides an intriguing insight into how strong associations with terrorism significantly affect public attitudes, more so than moderate or no associations. This underscores the powerful role of narrative and association in shaping public sentiment post-terrorism.

We used the following additional functions: [@broom], [@dotwhisker], [@cowplot], [@metafor] in [@citeR] to create @fig-reactions-to-terrorism.

```{r}
#| echo: false
#| warning: false
#| message: false

##### Fig3A.1 Overall ##### 
library(broom)
library(dotwhisker)
library(cowplot)
library(metafor)
############################
# 1) outgroup dataset
dat_outgroup <- dat[dat$PA_Category == 10 |
                      dat$PA_Category == 99, ]
# 2) conservative shift dataset
dat_conservatism <- dat[dat$PA_Category == 5 |
                          dat$PA_Category == 6 |
                          dat$PA_Category == 7 |
                          dat$PA_Category == 8 |
                          dat$PA_Category == 9 |
                          dat$PA_Category == 11, ]
# 3) rally-around-the-flag dataset
dat_rally <- dat[dat$PA_Category == 1 |
                   dat$PA_Category == 2 |
                   dat$PA_Category == 3 |
                   dat$PA_Category == 4, ]
######################################################
dat_outgroup$TerrorType2[dat_outgroup$Type==0] <- "No ideology"
dat_outgroup$TerrorType2[dat_outgroup$Type==1] <- "Islamist"
dat_outgroup$TerrorType2[is.na(dat_outgroup$TerrorType2)] <- "Other"
dat_outgroup$TerrorType2 <- as.factor(dat_outgroup$TerrorType2)
#convert into dummy variables
dat_outgroup$Islam <- ifelse(dat_outgroup$TerrorType2=="Islamist", yes=1, no=0)
dat_outgroup$No_Ideology <- ifelse(dat_outgroup$TerrorType2=="No ideology", yes=1, no=0)
dat_outgroup$Other_Ideology <- ifelse(dat_outgroup$TerrorType2=="Other", yes=1, no=0)
################################
dat_outgroup$Exp <- ifelse(dat_outgroup$TypeStudy==1, yes=1, no=0)
dat_outgroup$QuasiLong <- ifelse(dat_outgroup$TypeStudy==2 | 
                                   dat_outgroup$TypeStudy==4, yes=1, no=0)
dat_outgroup$Corr <- ifelse(dat_outgroup$TypeStudy==3, yes=1, no=0)
################################
dat_outgroup$Sample[dat_outgroup$GeneralPop==1] <- "General"
dat_outgroup$Sample[dat_outgroup$StudentPop==1] <- "Student"
dat_outgroup$Sample[is.na(dat_outgroup$Sample)] <- "Convenience"
dat_outgroup$Sample <- as.factor(dat_outgroup$Sample)
dat_outgroup$General <- ifelse(dat_outgroup$Sample=="General", yes=1, no=0)
dat_outgroup$Student <- ifelse(dat_outgroup$Sample=="Student", yes=1, no=0)
dat_outgroup$Convenience <- ifelse(dat_outgroup$Sample=="Convenience", yes=1, no=0)
################################
dat_outgroup$US <- ifelse(dat_outgroup$Country=="US", yes=1, no=0)
dat_outgroup$Israel <- ifelse(dat_outgroup$Country=="Israel", yes=1, no=0)
dat_outgroup$Other_c <- ifelse(dat_outgroup$US==0 
                               & dat_outgroup$Israel==0, yes=1, no=0)
############################
dat_outgroup$TargetSim[dat_outgroup$OA_Similarity==2] <- "A lot"
dat_outgroup$TargetSim[dat_outgroup$OA_Similarity==1] <- "A bit"
dat_outgroup$TargetSim[dat_outgroup$OA_Similarity==0] <- "No"
dat_outgroup$TargetSim <- as.factor(dat_outgroup$TargetSim)
#convert into dummy variables
dat_outgroup$Lot <- ifelse(dat_outgroup$TargetSim=="A lot", yes=1, no=0)
dat_outgroup$Bit <- ifelse(dat_outgroup$TargetSim=="A bit", yes=1, no=0)
dat_outgroup$No <- ifelse(dat_outgroup$TargetSim=="No", yes=1, no=0)

########################################
dat_conservatism$TerrorType2[dat_conservatism$Type==0] <- "No ideology"
dat_conservatism$TerrorType2[dat_conservatism$Type==1] <- "Islamist"
dat_conservatism$TerrorType2[is.na(dat_conservatism$TerrorType2)] <- "Other"
dat_conservatism$TerrorType2 <- as.factor(dat_conservatism$TerrorType2)
#convert into dummy variables
dat_conservatism$Islam <- ifelse(dat_conservatism$TerrorType2=="Islamist", yes=1, no=0)
dat_conservatism$No_Ideology <- ifelse(dat_conservatism$TerrorType2=="No ideology", yes=1, no=0)
dat_conservatism$Other_Ideology <- ifelse(dat_conservatism$TerrorType2=="Other", yes=1, no=0)
#############################
dat_conservatism$Exposure <- ifelse(dat_conservatism$TerrorMeasure=="Acts of violence", yes=1, no=0)
dat_conservatism$R_Exposure <- ifelse(dat_conservatism$TerrorMeasure=="Reported exposure", yes=1, no=0)
dat_conservatism$Threat <- ifelse(dat_conservatism$TerrorMeasure=="Threat", yes=1, no=0)
dat_conservatism$Emotions <- ifelse(dat_conservatism$TerrorMeasure=="Fear" | 
                                      dat_conservatism$TerrorMeasure=="Anger", yes=1, no=0)
dat_conservatism$Fear <- ifelse(dat_conservatism$TerrorMeasure=="Fear", yes=1, no=0)
dat_conservatism$Anger <- ifelse(dat_conservatism$TerrorMeasure=="Anger", yes=1, no=0)
dat_conservatism$Other_IV <- ifelse(dat_conservatism$TerrorMeasure=="Other", yes=1, no=0)
################################################################
#recode data
dat_conservatism$Design[dat_conservatism$TypeStudy==1] <- "Experiments"
dat_conservatism$Design[dat_conservatism$TypeStudy==2] <- "Quasi-Long"
dat_conservatism$Design[dat_conservatism$TypeStudy==3] <- "Correlations"
dat_conservatism$Design[dat_conservatism$TypeStudy==4] <- "Quasi-Long"
dat_conservatism$Design <- as.factor(dat_conservatism$Design)
#convert characters into dummy variables
dat_conservatism$Exp <- ifelse(dat_conservatism$TypeStudy==1, yes=1, no=0)
dat_conservatism$QuasiLong <- ifelse(dat_conservatism$TypeStudy==2 | 
                                       dat_conservatism$TypeStudy==4, yes=1, no=0)
dat_conservatism$Corr <- ifelse(dat_conservatism$TypeStudy==3, yes=1, no=0)
################################################
#recode data
dat_conservatism$Country2[dat_conservatism$Country=="US"] <- "US"
dat_conservatism$Country2[dat_conservatism$Country=="Israel"] <- "Israel"
dat_conservatism$Country2[is.na(dat_conservatism$Country2)] <- "Other"
dat_conservatism$Country2 <- as.factor(dat_conservatism$Country2)
#convert characters into dummy variables
dat_conservatism$US <- ifelse(dat_conservatism$Country=="US", yes=1, no=0)
dat_conservatism$Israel <- ifelse(dat_conservatism$Country=="Israel", yes=1, no=0)
dat_conservatism$Other_c <- ifelse(dat_conservatism$US==0 
                               & dat_conservatism$Israel==0, yes=1, no=0)
################################################

#recode data
dat_conservatism$Sample[dat_conservatism$GeneralPop==1] <- "General"
dat_conservatism$Sample[dat_conservatism$StudentPop==1] <- "Student"
dat_conservatism$Sample[is.na(dat_conservatism$Sample)] <- "Convenience"
dat_conservatism$Sample <- as.factor(dat_conservatism$Sample)
#convert characters into dummy variables
dat_conservatism$General <- ifelse(dat_conservatism$Sample=="General", yes=1, no=0)
dat_conservatism$Student <- ifelse(dat_conservatism$Sample=="Student", yes=1, no=0)
dat_conservatism$Convenience <- ifelse(dat_conservatism$Sample=="Convenience", yes=1, no=0)

################################################
set.seed(1234)
og_overall <- rma.mv(y=Fisher, V=Variance_F,
                     random = ~ 1 | ID_R/ID_ES_Unique, data=dat_outgroup,
                     method = "ML")
og_overall_df <- tidy(og_overall) # create data.frame of regression results

og_overall_df <- og_overall_df %>%  #re-label variable
  relabel_predictors(overall = "Overall Fisher's Z \n Correlation Coef." )           
og_overall_plot <- dwplot(og_overall_df, #plot
                          dot_args = list(size = 3),
                          whisker_args = list(size = 1),
                          vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 1))+
  ggtitle("Outgroup Hostility") +
  scale_color_grey() +
  xlim(-0.1, .25) +
  theme(axis.title.x=element_blank(),
        plot.margin=grid::unit(c(0,0,0,0), "mm"),
        axis.text.y = element_text(face = "bold",size = 14),
        axis.ticks.x=element_blank(),
        axis.text.x=element_blank(),
        plot.title = element_text(hjust = 0.5, size = 15, face = "bold"),
        panel.background = element_rect(fill = "grey90",
                                        colour = "grey90"),
        panel.grid = element_line(colour = "grey60"))

##### Fig3A.2 Terror type ##### 
#fit model and plot results
set.seed(1234)
og_terror <- rma.mv(y=Fisher, V=Variance_F, mods = cbind(Islam, Other_Ideology, No_Ideology),
                    intercept=F, 
                    random = ~ 1 | ID_R/ID_ES_Unique, data=dat_outgroup,
                    method = "ML")

og_terror_df <- tidy(og_terror) # create data.frame of regression results

og_terror_df <- og_terror_df %>%  #re-label variable
  relabel_predictors(c(Islam = "Islamist",
                       Other_Ideology  = "Other ideology",
                       No_Ideology  = "No ideology"))
og_terror_plot <- dwplot(og_terror_df, #plot
                         dot_args = list(size = 2),
                         whisker_args = list(size = 0.5),
                         vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 0.7)) +
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank(),
        plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  scale_color_grey() +
  xlim(-0.1, .25)

##### Fig3A.3 Research Design ##### 
#fit model and plot results
set.seed(1234)
og_design <- rma.mv(y=Fisher, V=Variance_F, mods = cbind(Exp, QuasiLong, Corr),
                    intercept=F, 
                    random = ~ 1 | ID_R/ID_ES_Unique, data=dat_outgroup,
                    method = "ML")

og_design_df <- tidy(og_design) # create data.frame of regression results

og_design_df <- og_design_df %>%  #re-label variable
  relabel_predictors(c(Exp = "Experiment",
                       Corr  = "Cross-sectional",
                       QuasiLong  = "Other designs"))
og_design_plot <- dwplot(og_design_df, #plot
                         dot_args = list(size = 2),
                         whisker_args = list(size = 0.5),
                         vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 0.7)) +
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank(),
        plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  scale_color_grey() +
  xlim(-0.1, .25)

##### Fig3A.4 Sample  ##### 
#fit model and plot results
set.seed(1234)
og_sample <- rma.mv(y=Fisher, V=Variance_F, mods = cbind(General, Student, Convenience),
                    intercept=F, 
                    random = ~ 1 | ID_R/ID_ES_Unique, data=dat_outgroup,
                    method = "ML")

og_sample_df <- tidy(og_sample) # create data.frame of regression results

og_sample_df <- og_sample_df %>%  #re-label variable
  relabel_predictors(c(General = "General population",
                       Student  = "Student sample",
                       Convenience  = "Convenience sample"))
og_sample_plot <- dwplot(og_sample_df, #plot
                         dot_args = list(size = 2),
                         whisker_args = list(size = 0.5),
                         vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 0.7)) +
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank(),
        plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  scale_color_grey() +
  xlim(-0.1, .25)

##### Fig3A.5 Geography ##### 
#fit model and plot results
set.seed(1234)
og_location <- rma.mv(y=Fisher, V=Variance_F, mods = cbind(US, Israel, Other_c),
                    intercept=F, 
                    random = ~ 1 | ID_R/ID_ES_Unique, data=dat_outgroup,
                    method = "ML")
og_location_df <- tidy(og_location) # create data.frame of regression results

og_location_df <- og_location_df %>%  #re-label variable
  relabel_predictors(c(US = "United States",
                       Israel  = "Israel",
                       Other_c  = "Other countries"))
og_location_plot <- dwplot(og_location_df, #plot
                         dot_args = list(size = 2),
                         whisker_args = list(size = 0.5),
                         vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 0.7)) +
  theme(plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  scale_color_grey() +
  xlim(-0.1, .25)

##### Fig3A.6 Guilt-by-Association ##### 
#fit model and plot results
set.seed(1234)
og_association <- rma.mv(y=Fisher, V=Variance_F, mods = cbind(Lot, Bit, No),
                      intercept=F, 
                      random = ~ 1 | ID_R/ID_ES_Unique, data=dat_outgroup,
                      method = "ML")

og_association_df <- tidy(og_association) # create data.frame of regression results

og_association_df <- og_association_df %>%  #re-label variable
  relabel_predictors(c(Lot = "Strong association",
                       Bit  = "Moderate association",
                       No  = "No association"))
og_association_plot <- dwplot(og_association_df, #plot
                           dot_args = list(size = 2),
                           whisker_args = list(size = 0.5),
                           vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 0.7)) +
  ggtitle("Guilt-By-Association") +
  scale_y_discrete(position = "left") +
  scale_color_grey() +
  theme(axis.title=element_text(face = "bold"),
        plot.margin=grid::unit(c(0,0,0,0), "mm"))+
  xlim(-0.1, .25)

##### Fig3A Outgroup Hostility Effect Sizes Plot ##### 
og_plots <- plot_grid(og_overall_plot, og_terror_plot, og_design_plot, og_sample_plot, og_location_plot,
                      og_association_plot,
                      ncol=1, nrow=6, 
                      rel_heights=c(0.8,1,1,1,1,1), align = "v")

# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
##### Fig3B. Conservative Shift Hypothesis ##### 
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
##### Fig3B.1 Overall ##### 
set.seed(1234)
cs_overall <- rma.mv(y=Fisher, V=Variance_F,
                     random = ~ 1 | ID_R/ID_ES_Unique, data=dat_conservatism,
                     method = "ML")
cs_overall_df <- tidy(cs_overall) # create data.frame of regression results

cs_overall_df <- cs_overall_df %>% 
  relabel_predictors(c(overall = "Overall Effect Size")) #re-label variable
cs_overall_plot <- dwplot(cs_overall_df, #plot
                          dot_args = list(size = 3),
                          whisker_args = list(size = 1),
                          vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 1))+
  ggtitle("Conservative Shift") +
  scale_color_grey() +
  xlim(-0.1, .25) +
  theme(axis.title.x=element_blank(),
        plot.margin=grid::unit(c(0,0,0,0), "mm"),
        axis.ticks=element_blank(),
        axis.text=element_blank(),
        plot.title = element_text(hjust = 0.5, size = 15, face = "bold"),
        panel.background = element_rect(fill = "grey90",
                                        colour = "grey90"),
        panel.grid = element_line(colour = "grey60"))

##### Fig3B.2 Terror type ##### 
#fit model and plot results
set.seed(1234)
cs_terror <- rma.mv(y=Fisher, V=Variance_F, mods = cbind(Islam, Other_Ideology, No_Ideology),
                    intercept=F, 
                    random = ~ 1 | ID_R/ID_ES_Unique, data=dat_conservatism,
                    method = "ML")

cs_terror_df <- tidy(cs_terror) # create data.frame of regression results

cs_terror_df <- cs_terror_df %>%  #re-label variable
  relabel_predictors(c(Islam = "Islamist",
                       Other_Ideology  = "Other Ideology",
                       No_Ideology  = "No Ideology"))
cs_terror_plot <- dwplot(cs_terror_df, #plot
                         dot_args = list(size = 2),
                         whisker_args = list(size = 0.5),
                         vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 0.7)) +
  theme(plot.title = element_text(size = 14), axis.text=element_blank(), axis.ticks=element_blank(),
        plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  scale_color_grey() +
  xlim(-0.1, .25)

##### Fig3B.3 Research Design ##### 
#fit model and plot results
set.seed(1234)
cs_design <- rma.mv(y=Fisher, V=Variance_F, mods = cbind(Exp, QuasiLong, Corr),
                    intercept=F, 
                    random = ~ 1 | ID_R/ID_ES_Unique, data=dat_conservatism,
                    method = "ML")
cs_design_df <- tidy(cs_design) # create data.frame of regression results

cs_design_df <- cs_design_df %>%  #re-label variable
  relabel_predictors(c(Exp = "Experiments",
                       Corr  = "Cross-Sectional",
                       QuasiLong  = "Other Designs"))
cs_design_plot <- dwplot(cs_design_df, #plot
                         dot_args = list(size = 2),
                         whisker_args = list(size = 0.5),
                         vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 0.7)) +
  theme(plot.title = element_text(size = 14), axis.text=element_blank(), 
        axis.ticks=element_blank(),
        plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  scale_color_grey() +
  xlim(-0.1, .25)

##### Fig3B.4 Sample  ##### 
#fit model and plot results
set.seed(1234)
cs_sample <- rma.mv(y=Fisher, V=Variance_F, mods = cbind(General, Student, Convenience),
                    intercept=F, 
                    random = ~ 1 | ID_R/ID_ES_Unique, data=dat_conservatism,
                    method = "ML")

cs_sample_df <- tidy(cs_sample) # create data.frame of regression results

cs_sample_df <- cs_sample_df %>%  #re-label variable
  relabel_predictors(c(General = "General Population",
                       Student  = "Student Samples",
                       Convenience  = "Convenience Samples"))
cs_sample_plot <- dwplot(cs_sample_df, #plot
                         dot_args = list(size = 2),
                         whisker_args = list(size = 0.5),
                         vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 0.7)) +
  theme(plot.title = element_text(size = 14), 
        axis.text=element_blank(), axis.ticks=element_blank(),
        plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  scale_color_grey() +
  xlim(-0.1, .25)

##### Fig3B.5 Geography ##### 
#fit model and plot results
set.seed(1234)
cs_location <- rma.mv(y=Fisher, V=Variance_F, mods = cbind(US, Israel, Other_c),
                      intercept=F, 
                      random = ~ 1 | ID_R/ID_ES_Unique, data=dat_conservatism,
                      method = "ML")
cs_location_df <- tidy(cs_location) # create data.frame of regression results

cs_location_df <- cs_location_df %>%  #re-label variable
  relabel_predictors(c(US = "United States",
                       Israel  = "Israel",
                       Other_c  = "Other Countries"))
cs_location_plot <- dwplot(cs_location_df, #plot
                           dot_args = list(size = 2),
                           whisker_args = list(size = 0.5),
                           vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 0.7)) +
  theme(plot.title = element_text(size = 14), 
        axis.text.y=element_blank(), axis.ticks.y=element_blank(),
        plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  scale_color_grey() +
  xlim(-0.1, .25)

##### Fig3B Conservative Shift Effect Sizes Plot ##### 
cs_plots <- plot_grid(cs_overall_plot, cs_terror_plot, cs_design_plot, cs_sample_plot, cs_location_plot, 
                      ncol=1, nrow=6, 
                      rel_heights=c(0.8,1,1,1,1,1), align = "v")

```

```{r fig.width=15, fig.height=16}
#| label: fig-reactions-to-terrorism
#| fig-cap: Relationship between Terrorism and Political Attitudes Conditional on Substantive and Methodological Factors
#| echo: false
#| warning: false
#| message: false

# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
##### Fig3C. Rally Effects Hypothesis ##### 
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
##### Fig3C.1 Overall ##### 
#recode data
dat_rally$TerrorType2[dat_rally$Type==0] <- "No ideology"
dat_rally$TerrorType2[dat_rally$Type==1] <- "Islamist"
dat_rally$TerrorType2[is.na(dat_rally$TerrorType2)] <- "Other"
dat_rally$TerrorType2 <- as.factor(dat_rally$TerrorType2)
#convert into dummy variables
dat_rally$Islam <- ifelse(dat_rally$TerrorType2=="Islamist", yes=1, no=0)
dat_rally$No_Ideology <- ifelse(dat_rally$TerrorType2=="No ideology", yes=1, no=0)
dat_rally$Other_Ideology <- ifelse(dat_rally$TerrorType2=="Other", yes=1, no=0)

####################################

#convert characters into dummy variables
dat_rally$Exposure <- ifelse(dat_rally$TerrorMeasure=="Acts of violence", yes=1, no=0)
dat_rally$R_Exposure <- ifelse(dat_rally$TerrorMeasure=="Reported exposure", yes=1, no=0)
dat_rally$Threat <- ifelse(dat_rally$TerrorMeasure=="Threat", yes=1, no=0)
dat_rally$Emotions <- ifelse(dat_rally$TerrorMeasure=="Fear" | 
                                      dat_rally$TerrorMeasure=="Anger", yes=1, no=0)
dat_rally$Fear <- ifelse(dat_rally$TerrorMeasure=="Fear", yes=1, no=0)
dat_rally$Anger <- ifelse(dat_rally$TerrorMeasure=="Anger", yes=1, no=0)
dat_rally$Other_IV <- ifelse(dat_rally$TerrorMeasure=="Other", yes=1, no=0)

############################

#recode data
dat_rally$Design[dat_rally$TypeStudy==1] <- "Experiments"
dat_rally$Design[dat_rally$TypeStudy==2] <- "Quasi-Long"
dat_rally$Design[dat_rally$TypeStudy==3] <- "Correlations"
dat_rally$Design[dat_rally$TypeStudy==4] <- "Quasi-Long"
dat_rally$Design <- as.factor(dat_rally$Design)
#convert characters into dummy variables
dat_rally$Exp <- ifelse(dat_rally$TypeStudy==1, yes=1, no=0)
dat_rally$QuasiLong <- ifelse(dat_rally$TypeStudy==2 | 
                                dat_rally$TypeStudy==4, yes=1, no=0)
dat_rally$Corr <- ifelse(dat_rally$TypeStudy==3, yes=1, no=0)

####################################

#recode data
dat_rally$Sample[dat_rally$GeneralPop==1] <- "General"
dat_rally$Sample[dat_rally$StudentPop==1] <- "Student"
dat_rally$Sample[is.na(dat_rally$Sample)] <- "Convenience"
dat_rally$Sample <- as.factor(dat_rally$Sample)
#convert characters into dummy variables
dat_rally$General <- ifelse(dat_rally$Sample=="General", yes=1, no=0)
dat_rally$Student <- ifelse(dat_rally$Sample=="Student", yes=1, no=0)
dat_rally$Convenience <- ifelse(dat_rally$Sample=="Convenience", yes=1, no=0)
####################################
#recode data
dat_rally$Country2[dat_rally$Country=="US"] <- "US"
dat_rally$Country2[dat_rally$Country=="Israel"] <- "Israel"
dat_rally$Country2[is.na(dat_rally$Country2)] <- "Other"
dat_rally$Country2 <- as.factor(dat_rally$Country2)
#convert characters into dummy variables
dat_rally$US <- ifelse(dat_rally$Country=="US", yes=1, no=0)
dat_rally$Israel <- ifelse(dat_rally$Country=="Israel", yes=1, no=0)
dat_rally$Other_c <- ifelse(dat_rally$US==0 
                                   & dat_rally$Israel==0, yes=1, no=0)
####################################

set.seed(1234)
rf_overall <- rma.mv(y=Fisher, V=Variance_F,
                     random = ~ 1 | ID_R/ID_ES_Unique, data=dat_rally,
                     method = "ML")
rf_overall_df <- tidy(rf_overall) # create data.frame of regression results

>>>>

```{r }
#| label: fig-terrorism-trend
#| fig-cap: Summary of Data Included in theMeta-Analysis
#| echo: false
#| warning: false
#| message: false
#| out.width: "90%"  # Adjust to fit the page
#| out.height: "90%"  # Adjust to fit the page

knitr::include_graphics("../../outputs/figures/Figure1.jpeg")
```

```{r}
#| label: fig-reactions-to-terrorism
#| fig-cap: Relationship between Terrorism and Political Attitudes Conditional on Substantive and Methodological Factors
#| echo: false
#| warning: false
#| message: false
#| out.width: "90%"  # Adjust to fit the page
#| out.height: "90%"  # Adjust to fit the page
knitr::include_graphics("../../outputs/figures/Figure2.jpeg")
```

@@
